### 2023-10-16 ms.qmd
Updates

@fig-fig1

>>>>

# Load packages
pacman::p_load(tidyverse, flextable, brms, ggplot2)

# Load data
	data  <-  read.csv("./data/Learning.csv")
```

```{r, dataclean}
#| label: dataclean
#| echo: false
#| warning: false

# Removing individuals who did not participate (more than 15 NAs)
data_associative <- data %>%
  group_by(lizard_id) %>%
  filter(sum(is.na(FC_associative)) <= 15) %>%
  ungroup()
data_associative <- as.data.frame(data_associative)

# Removing trials [36-40] (Only in associative)
data_associative <- data_associative %>%
group_by(lizard_id) %>%
filter(trial_associative <= 35) %>%
ungroup()
data_associative <- as.data.frame(data_associative)

# Standarize data by trial (i.e. make the first trial where each individual participated their trial 1)

data_associative <- data_associative %>%
  group_by(lizard_id) %>%
  mutate(
    first_non_na = min(which(!is.na(FC_associative))),
    Associative_Trial = ifelse(!is.na(first_non_na),trial_associative - first_non_na + 1, trial_associative))%>%
    filter(Associative_Trial >= 1) %>%
   ungroup()

data_associative <- as.data.frame(data_associative)
write.csv(data_associative, file= "./output/Checking/data_associative.csv")

# Split data
deli_associative <- data_associative %>% filter (species == "delicata")
guich_associative <- data_associative %>% filter (species == "guichenoti")
